---
title: The Size of the Corpus
author: Will Hanley
date: '2019-05-28'
slug: the-size-of-the-corpus
categories: []
tags:
  - word count
keywords: ~
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Journal word count over time

These code blocks are repetitive, repeating the same steps for each of three journals. It might be good to figure out how to do all three in one step.

First, load text of all files
```{r load text}
library(xml2)

bslc_files <- dir("bslc/bslc-issues", full.names = TRUE)
bslc_text <- c()
for (f in bslc_files) {
  bslc_text <- c(bslc_text, gsub("\\s+", " ", paste(xml_text(xml_find_all(read_xml(f), "//text()")), collapse=" ")))
}

clunet_files <- dir("clunet/clunet-issues", full.names = TRUE)
clunet_text <- c()
for (f in clunet_files) {
  clunet_text <- c(clunet_text, gsub("\\s+", " ", paste(xml_text(xml_find_all(read_xml(f), "//text()")), collapse=" ")))
}

rdilc_files <- dir("rdilc/rdilc-issues", full.names = TRUE)
rdilc_text <- c()
for (f in rdilc_files) {
  rdilc_text <- c(rdilc_text, gsub("\\s+", " ", paste(xml_text(xml_find_all(read_xml(f), "//text()")), collapse=" ")))
}
```

Tokenize the words, then count them:
```{r tokenize, results='hide'}
library(tokenizers)

clunet_words <- tokenize_words(clunet_text)
sapply(clunet_words, length)
bslc_words <- tokenize_words(bslc_text)
sapply(bslc_words, length)
rdilc_words <- tokenize_words(rdilc_text)
sapply(rdilc_words, length)
```

I prepared separate metadata summaries about each journal, drawing year and date from the TEI header of each file. These summaries will probably be useful in future steps. For now, get and use date metadata about every issue:
```{r metadata, message=FALSE}
library(tidyverse)

bslc_metadata <- read_csv("bslc/bslc-summary.csv")
clunet_metadata <- read_csv("clunet/clunet-summary.csv")
rdilc_metadata <- read_csv("rdilc/rdilc-summary.csv")
```

Now, produce a tibble for each journal, with each issue (there was more than one per year) its own observation. This tibble lists the issue, word count, and abbreviated title of the journal.
```{r tibbles}
bslc_word_count <- tibble(year = bslc_metadata$year, words = sapply(bslc_words, length), journal = "bslc")
clunet_word_count <- tibble(year = clunet_metadata$year, words = sapply(clunet_words, length), journal = "clunet")
rdilc_word_count <- tibble(year = rdilc_metadata$year, words = sapply(rdilc_words, length), journal = "clunet")
```

Now cluster word counts by year:
```{r cluster by year}
clunet_word_count_year <- clunet_word_count %>% 
  group_by(year) %>% 
  summarise(words = sum(words), journal = "clunet")
bslc_word_count_year <- bslc_word_count %>% 
  group_by(year) %>% 
  summarise(words = sum(words), journal = "bslc")
rdilc_word_count_year <- rdilc_word_count %>% 
  group_by(year) %>% 
  summarise(words = sum(words), journal = "rdilc")
```

Put all three journals in a single tibble:
```{r single tibble, message=FALSE}
journals_count <- full_join(clunet_word_count_year, bslc_word_count_year)
journals_count <- full_join(journals_count, rdilc_word_count_year)
```

Plot the results as points and smoothing line
```{r plot}
p <- ggplot(data = journals_count, mapping = aes(x = year, y = words, color = journal))
p + geom_point() + geom_smooth()
```

Plot the results as a streamgraph:
```{r streamgraph}
library(streamgraph)
streamgraph(journals_count, key="journal", value="words", date="year", offset="zero") 
```
